Accuracy and precision of zero-heat-flux temperature monitoring

### 2020-01-06 manuscript/manuscript.Rmd
submission to a&a

```{r global_options, include=FALSE}
knitr::opts_chunk$set(include=FALSE,
                      echo=FALSE, warning=FALSE, message=FALSE)
library(dplyr)
library(ggprisma) # https://github.com/awconway/ggprisma
library(kableExtra)
library(knitr)
library(magrittr)
source("R/loa_maker.R")
source("R/meta.R")
```
\pagebreak

@@

Summary statement: Clinicians should consider the potential that a temperature measurement from a zero-heat-flux thermometer could be as much as 1°C higher or lower than core temperature.

@@

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(include=FALSE,
                      echo=FALSE, warning=FALSE, message=FALSE)
library(dplyr)
library(ggprisma) # https://github.com/awconway/ggprisma
library(kableExtra)
library(knitr)
library(magrittr)
source("R/loa_maker.R")
source("R/meta.R")
```

@@

@@

### Key points

**Question:** How accurate are temperature measurements from zero-heat-flux temperature monitors?

**Findings:** Population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C.

**Meaning:** Zero-heat-flux temperature monitoring would not be appropriate if a difference in temperature of 1°C is important to detect for the given clinical situation.
